The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-05-03 Paper.Rmd
modified

In addition to [basic unit tests](https://github.com/sghosh89/BIVAN/blob/master/Tests.Rmd), we 
also tested our statistics in Fig. \ref{fig_stat_image}(B - D) by testing whether $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, and 
$\Dsq_u-\Dsq_l$ revealed the asymmetry of tail dependence known to be present in data simulated
from Clayton copulas (for details see Appendix \ref{SM-Test_npa_stat}).

>>>>

In addition to [basic unit tests](https://github.com/sghosh89/BIVAN/blob/master/Tests.Rmd), we also tested our statistics by testing whether $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, and $\Dsq_u-\Dsq_l$ revealed the asymmetry of tail dependence known to be present in data simulated from various copulas. Fig. \ref{fig_stat_image}(B - D) represent the results for Clayton copulas with $n=35$ data points and $100$ simulations (for details see Appendix \ref{SM-Test_npa_stat}).
